Global code motion of congruent instructions

### 2017-11-08 cgo/paper.tex
codehoisting

\begin{verbatim}
int doCodeHoisting()
  Sort VNs in ascending order

  for each instruction with the same VN
      Find its post-dominance-frontier (PDF)
      Insert the CHI-node at PDF

>>>>

\begin{verbatim}
int doCodeHoisting(VNs)
  // VNs = map (VN -> list of I with value VN)
  Sort VNs in ascending order

  for each VN in VNs
    for each instruction with the same VN
      Find its post-dominance-frontier (PDF)
      Insert the CHI-node at PDF
